Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-17 paper/main.tex
main

\begin{wrapfigure}{r}{5.2cm}
\begin{tabular}{|r@{\,}r@{\,}lr|r@{\,}r@{\,}lr|} \hline
\tt 0 &--& \tt 50    & \Runbina & \tt 501 &--&\tt 1000   & \Runbine\\
\tt 51 &--& \tt 100  & \Runbinb & \tt 1001 &--&\tt 1500  & \Runbinf\\
\tt 101 &--& \tt 250 & \Runbinc & \tt 1501 &--&\tt 2000  & \Runbing\\
\tt 251 &--& \tt 500 & \Runbind & \tt 2001 &--& \tt 3000 & \Runbinh\\\hline
\end{tabular}
\caption{Normalized invocations} \label{tab:callsitesnormalized}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{5.2cm}
  \vspace{-8mm}
    \includegraphics[width=.4\textwidth]{calls_per_run_per_call_site}
    \caption{Normalized invocations
      (small)} \label{fig:callsitesnormalized}
    \vspace{-3mm}
\end{wrapfigure}

@@

@@

\mypara{Eval Arguments.} Figure~\ref{fig:eval-expression-kind} breaks
down the expressions passed to \eval by R data type. It separates the
core packages from CRAN as they have different characteristics. In
core, XXX036\% of arguments in core are expressions. Whereas, in CRAN
package XXX037\% are expressions. When the argument is not an
expression, it is a value. Values are trivial for \eval as they are
returned unchanged. \PackageEnvironmentInputEvalCallPerc of CRAN
arguments are environments. This is an anomaly as only four \eval
call sites dominate this result:
\begin{compactitem}[$-$]
\item \c{ggplot2::ggproto} contributes to 99.9\% of package \eval
  calls that receive environments as input.
\item \c{R6::generator_funs} function contributes to only 936 \eval
  calls and implements the same functionality as \c{ggplot2::ggproto}
  but for the \emph{R6} OOP system.
\item \c{future::backtrace} function applies \eval to a future object
  which is implemented as an environment. This is called only once.
\item \c{RModel::str.RMmodel} function overloads the core \c{str}
  method for its \c{RModel} objects and maps \eval exactly like
  \c{str}. This is called only once.
\end{compactitem}

\begin{figure}[!h]
  \centering
  \includegraphics[width=\columnwidth]{eval-expression-kind}
  \caption{Type of Expression passed to \eval} \label{fig:eval-expression-kind}
\end{figure}

>>>>

\begin{wrapfigure}{r}{5.8cm}
  \begin{tabular}{|r@{\,}r@{\,}l@{\,}r|r@{\,}r@{\,}l@{}r|} \hline
\multicolumn{3}{|c}{\small\#calls} &\small\#sites &
\multicolumn{3}{c}{\small\#calls} &\small\#sites \\\hline
\tt 0 &--& \tt 50    & \Runbina & \tt 501 &--& \tt 1000   & \Runbine\\
\tt 51 &--& \tt 100  & \Runbinb & \tt 1001 &--& \tt 1500  & \Runbinf\\
\tt 101 &--& \tt 250 & \Runbinc & \tt 1501 &--& \tt 2000  & \Runbing\\
\tt 251 &--& \tt 500 & \Runbind & \tt 2001 &--& \tt 3000 & \Runbinh\\\hline
\end{tabular}
\caption{Normalized invocations} \label{tab:callsitesnormalized}
\end{wrapfigure}

@@

\medskip

\begin{wrapfigure}{r}{5.5cm}
  \vspace{-8mm}
    \includegraphics[width=.4\textwidth]{calls_per_run_per_call_site}
    \caption{Normalized invocations
      (small)} \label{fig:callsitesnormalized}
   \vspace{-8mm}
\end{wrapfigure}

@@

Analysis of the arguments passed to \eval reveals that XXX are of kind
\c{symbol} (single variables), XXX are \c{language} (an internal R
type roughly corresponding to a single expression), and XXX are
\c{expression} (one or more statements). The remaining arguments are R
values which are returned unchanged.

@@
